\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-10 related-work.tex
reply

\noindentparagraph{Solutions to the expression problem} abound\EDJ{I have been meaning to ask but is this ``abound'' you intentionally put outside of the boldfont?}.
Almost all solutions involve some form of either explicit or implicit parameterization.
Our approach is the first that applies family polymorphism~\cite{ernst2001family},
an idea found in the context of OO programming,
to the context of mechanized proofs.
%Families in \Lang are second-class, in that they are not considered
%terms by themselves.
%Families as modeled in \TT (namely linkages) are first-class and thus more flexible.\EDJ{A more unified way is to consider Coq's Family (our surface syntax) second class corresponds to Inheritance Judgement/Linkage Transformer (secondclass in type theory). Linkage transformer is the helper function to construct first class linkage easily. Even non-derived (surface syntax) family can be considered in this way because they are just inheritance on empty family.}
%The distinction corresponds to class-based vs.\ object-base family
%polymorphism as summarized before~\cite{cdnw07-tribe}.

>>>>

\noindentparagraph{Solutions to the expression problem} \!abound.\EDJ{I have been meaning to ask but is this ``abound'' you intentionally put outside of the boldfont?}\YZreply{Yes}
Almost all involve some form of either explicit or implicit parameterization
as extensibility hooks.
Our approach is the first that applies family polymorphism~\cite{ernst2001family},
an idea from the context of OO languages,
to the context of mechanized proofs.
%Families in \Lang are second-class, in that they are not considered
%terms by themselves.
%Families as modeled in \TT (namely linkages) are first-class and thus more flexible.\EDJ{A more unified way is to consider Coq's Family (our surface syntax) second class corresponds to Inheritance Judgement/Linkage Transformer (secondclass in type theory). Linkage transformer is the helper function to construct first class linkage easily. Even non-derived (surface syntax) family can be considered in this way because they are just inheritance on empty family.}
%The distinction corresponds to class-based vs.\ object-base family
%polymorphism as summarized before~\cite{cdnw07-tribe}.
